Three 38 Million Year Old Mini-Neptunes from Kepler, TESS, and Gaia

### 2022-03-08 papers/ms.tex
paper: add kinematic context

@@

>>>>

%FIXME WORDING OF THIS PARAGRAPH NEEDS WORK.  ALSO, WHERE DO YOU PUT
%THE CONTEXT RE CLUSTERS?
Understanding the formation and evolution of stellar clusters is
similarly an emerging frontier in analyses of star formation and
cluster evolution.  In particular, it is understood that most embedded
clusters disperse within a few tens of millions of years after forming
their first stars (CITE).  The discovery of tidal tails (CITE CITE)...
streams (CITE Meingast18, Curtis19), etc...  Connect to moving groups
(CITE Gagne 21).  What are the typical densities for star formation?
How does gas expulsion and the SFE affect cluster morphology?  {\bf
FIXME}

@@

Our focus is on a region of the Galaxy roughly 200 to 500 parsecs from
the Sun, above the galactic plane, and spanning galactic longitudes of
roughly $40^\circ$ to $100^\circ$ degrees.  A direct query of the Gaia
archive imposing these constraints yields $\approx3.4\times10^7$
sources.  Imposing the cuts suggested by \citet[][Appendix
B]{GaiaCollaboration2018} on the photometric signal to noise ratio,
the number of visibility periods used, the astrometric $\chi^2$ of the
single-source solution, the $G_{\rm BP}-G_{\rm RP}$ color excess
factor and the parallax precision ($\varpi/\sigma_\varpi>5$) yields
$\approx5.0\times10^6$ sources.

Imposing a thin slice in color-absolute magnitude space around the
pre-main-sequence of the $\delta$ Lyr cluster's previously established
$\approx$40 Myr locus, and imposing kinematics cut for $-8 < v_b /
{\rm km\,s^{-1}} < 0$ and $-15 < v_{l'} / {\rm km\,s^{-1}} < 15$,
where $l'=l\cos b$, yields $\approx 5.2\times10^3$ sources.  These
objects are all in the range BP-RP 1.5 to 3.2, so roughly K5V to
M4.5V, or $\approx$0.2 to 0.7 solar masses.  Much more manageable, but
according to IMF arguments, missing at least a factor of two in mass
of any clusters.

In XYZ, and in tangential velocity space, these five thousand sources
are visually clustered in between a few to a dozen groups, depending
on the characteristic size and velocity scales of interest.  The first
suggestion that these objects could all be part of a monolithic
structure, to our knowledge, came from the manual grouping that was
performed between them by \citet{KounkelCovey2019} when defining the
structure they dubbed ``Theia~73''.  Different subsets of these stars
have however previously been noticed and studied.  They include the
$\delta$ Lyr cluster, also known as Stephenson-1
\citep{stephenson_possible_1959}, which comprises a major grouping
around $(l,b)=(68^\circ,15^\circ)$, with typical velocities $(v_{l'},
v_b)=(-4.5{\rm \kms},-4{\rm \kms})$.  Another individual component
that has previously been recognized is RSG-5 \citep{roser_nine_2016}.
This group is at roughly $(l,b)=(83^\circ,6^\circ)$, with velocities
$(v_{l'}, v_b)=(+5.5{\rm \kms},-3.5{\rm \kms})$.  Most of the other
subclusters, including CH-2, and those in Cep-Cyg and Cerberus are too
small or dispersed to have previously been analyzed in great detail.
